Supplementary information

### 2019-11-18 manuscript/supplementary.Rmd
tables and figures temporarily rendered separate from the manuscript
added rf model tuning
added decline index plot
removed code chunks from supplementary
added PDI lime analysis plot to supplementary

---
output: 
  pdf_document:
    keep_tex: no
---

## Supplementary information

@@

@@

>>>>

---
title: Supplementary information
output: 
  pdf_document:
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

@@

```{r decline_index_plot}
loadd(decline_indexes_plot)

decline_indexes_plot
```

@@

```{r modelTuningResultsPlot}
loadd(rf_tune_plot)

rf_tune_plot
```

```{r PDIlimeAnalysisPlot}
loadd(PDI_lime_analysis_plot)

PDI_lime_analysis_plot
```
